Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-05-14 sections/acknowledgements.tex
Shortening titles in acknowledgements

\noindent Special thanks to Scott Austin, Ph.D. (Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas), Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator), and Shane Ayotte (UCA Mathematics Student).

>>>>

\noindent Special thanks to Scott Austin, Ph.D. (Associate Professor of Astronomy and Physics, UCA), Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics), and Shane Ayotte (UCA Mathematics Student).
